A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-08-09 poster/poster.tex
Poster tweaks

\useblockstyle[bodyverticalshift=-1cm, roundedcorners=1]{Default}

@@

\begin{columns}
\column{1}
{
    \colorlet{blockbodybgcolor}{uofgcobalt}
    \colorlet{blocktitlebgcolor}{uofgcobalt}
    \block[bodyverticalshift=0.5cm, bodyinnersep=3mm]{}{
        \centering\begin{minipage}{0.94\textwidth}
            \Large We introduce a new branch and bound algorithm for the \textbf{maximum common
            subgraph} and \textbf{maximum common connected subgraph} problems which is based
            around vertex labelling and partitioning. Our method resembles
            a constraint programming approach, but uses a novel compact
            domain store to reduce
            the memory and computation requirements.  Experiments
            show a speedup of more than an order of magnitude over the state of the
            art, and demonstrate that we can operate on much larger graphs without
            running out of memory.
%            We show how to generate \textbf{really hard} random instances for \textbf{subgraph
%            isomorphism} problems. For the non-induced variant, we predict and observe a phase
%            transition between satisfiable and unsatisfiable instances, with a corresponding
%            complexity peak seen in \textbf{three different solvers}. For the induced variant, much
%            richer behaviour is observed, and \textbf{constrainedness} gives a better measure of
%            difficulty than does proximity to a phase transition. We also discuss \textbf{variable
%            and value ordering} heuristics, and their relationship to the \textbf{expected number of
%            solutions}.
        \end{minipage}
        \vspace*{0.4cm}
    }
}
\end{columns}

@@

\block{The Maximum Common Subgraph Problem}{
\begin{wrapfigure}[7]{r}{0.48\linewidth}
    \begin{flushright}\begin{tikzpicture}[scale=1.6]%{{{
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (Na) at (1,  0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (Nb) at (1, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (Nc) at (1, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (Nd) at (3, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (Ne) at (3, -2)
        {\vphantom{0}};

@@

        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (N1) at (7.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N2) at (9.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (N3) at (7.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N4) at (9.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (N5) at (7.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (N6) at (9.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N7) at (5.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N8) at (5.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N9) at (5.5, -4) {\vphantom{0}};

@@

The \textbf{maximum common subgraph} family of problems involves finding a large
graph which is isomorphic to subgraphs of two input graphs.
Such problems have arisen in molecular science---where graphs often represent
molecules---malware detection, source code analysis, and computer vision.

@@

Using depth-first search, the \McSplit\ algorithm builds up an injective mapping from a subset
of vertices in the pattern graph to a subset of vertices in the target graph.  
Remaining vertices are partitioned into \textbf{label classes} according to the set of mapped
vertices to which they are adjacent; each pattern-graph vertex may only be mapped to target-graph
vertices in the same label class.  We thus avoid
the need for a conventional domain store in which the possible mappings for each
vertex are stored explicitly.

Straightforward extensions can be made to the algorithm to handle edge- and vertex-labelled graphs,
and directed graphs.  We can also solve the problem where the subgraph must be connected,
by branching only on vertices adjacent to at least one currently-mapped vertex.
}

\block{Relationship to Prior Constraint Programming Encodings}{

@@

    Why is this?  The key
    observation is that \McSplit\ may be considered to be a different version of the CP-FC algorithm,
    using an unconventional domain store and more efficient filtering algorithms.
    We explore this relationship in the paper.

@@

@@

    \vspace*{3em}

@@

    \vspace*{3em}

}

@@

\block{See the Paper For\ldots}{
    \begin{itemize}
        \item ~ A walk-through of the algorithm
        \item ~ How to extend the algorithm to handle vertex and edge labels
        \item ~ Additional experimental results
    \end{itemize}
}

\block{Future Work}{
    \begin{itemize}
        \item ~ Better branching heuristics
        \item ~ Branching on vertices in both graphs
        \item ~ Applying the partitioning data structure to other problems
    \end{itemize}
    \vspace*{0.25em}
}

{
    \colorlet{blockbodybgcolor}{uofgsandstone!80!white}
    \colorlet{blocktitlebgcolor}{uofgsandstone!80!white}
    \block[bodyverticalshift=-0.5cm]{}{
        This work was supported by the Engineering and Physical Sciences Research Council [grant
        number EP/K503058/1]. \hfill \texttt{\textcolor{white}{c.mccreesh.1@research.gla.ac.uk}}
    }
}

>>>>

\useblockstyle[bodyverticalshift=-1cm, roundedcorners=0]{Default}

@@

\begin{columns}
\column{1}
{
    \colorlet{blockbodybgcolor}{uofgcobalt}
    \colorlet{blocktitlebgcolor}{uofgcobalt}
    \block[bodyverticalshift=0.5cm, bodyinnersep=3mm]{}{
        \centering\begin{minipage}{0.94\textwidth}
            \Large We introduce a new \textbf{branch and bound} algorithm for the \textbf{maximum common
            subgraph} and \textbf{maximum common connected subgraph} problems which is based
            around vertex labelling and partitioning. Our method resembles
            a constraint programming approach, but uses a novel compact
            domain store to reduce
            the memory and computation requirements.  Experiments
            show a \textbf{speedup of more than an order of magnitude} over the state of the
            art, and demonstrate that we can operate on \textbf{much larger graphs} without
            running out of memory.
%            We show how to generate \textbf{really hard} random instances for \textbf{subgraph
%            isomorphism} problems. For the non-induced variant, we predict and observe a phase
%            transition between satisfiable and unsatisfiable instances, with a corresponding
%            complexity peak seen in \textbf{three different solvers}. For the induced variant, much
%            richer behaviour is observed, and \textbf{constrainedness} gives a better measure of
%            difficulty than does proximity to a phase transition. We also discuss \textbf{variable
%            and value ordering} heuristics, and their relationship to the \textbf{expected number of
%            solutions}.
        \end{minipage}
        \vspace*{0.4cm}
    }
}
\end{columns}

@@

\block{The Maximum Common Subgraph Problem}{
\begin{wrapfigure}[7]{r}{0.47\linewidth}
    \begin{flushright}\begin{tikzpicture}[scale=1.6]%{{{
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (Na) at (1,  0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (Nb) at (1, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (Nc) at (1, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (Nd) at (3, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (Ne) at (3, -2)
        {\vphantom{0}};

@@

        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (N1) at (7.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N2) at (9.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (N3) at (7.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N4) at (9.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (N5) at (7.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=8pt, font=\bfseries] (N6) at (9.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N7) at (5.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N8) at (5.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=8pt, font=\bfseries] (N9) at (5.5, -4) {\vphantom{0}};

@@

The \textbf{maximum common subgraph} family of problems involves finding a large
graph that appears in each of two input graphs.
Such problems have arisen in molecular science---where graphs often represent
molecules---malware detection, source code analysis, and computer vision.

@@

Using depth-first search, the \McSplit\ algorithm builds up an injective mapping from a subset
of vertices in the pattern graph to a subset of vertices in the target graph.  
Remaining vertices are partitioned into \textbf{label classes} according to the set of mapped
vertices to which they are adjacent; each pattern-graph vertex may only be mapped to target-graph
vertices in the same label class.  We thus avoid
the need for a conventional domain store in which the possible mappings for each
vertex are stored explicitly.  
}

\block{The Relationship to Constraint Programming}{

@@

    Why is this?  The key
    observation is that \McSplit\ may be considered to be a different version of the CP-FC algorithm,
    using an unconventional domain store and more efficient filtering algorithms.
    This is possible because in the CP model, \textbf{any two domains are either identical
    or disjoint}, excluding $\bot$.  We explore this relationship further in the paper.

    \vspace*{1em}

@@

\block{See the Paper For\ldots}{
    \begin{itemize}
        \item ~ How to extend the algorithm to handle vertex and edge labels
        \item ~ Additional experimental results
    \end{itemize}
}

@@

@@

    \begin{center}
        \small
        \input{gen-graph-sip-cumulative}
    \end{center}
}

@@

%\begin{columns}
%\column{0.5}
%
%\column{0.5}
%
%%\block{Future Work}{
%%    \begin{itemize}
%%        \item ~ Branching on vertices in both graphs
%%        \item ~ Applying the partitioning data structure to other problems
%%    \end{itemize}
%%    \vspace*{0.25em}
%%}
%
%\end{columns}

{
    \colorlet{blockbodybgcolor}{uofgsandstone!80!white}
    \colorlet{blocktitlebgcolor}{uofgsandstone!80!white}
    \block[bodyverticalshift=-0.5cm]{}{
        This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and
        EP/M508056/1]. \hfill \texttt{\textcolor{white}{j.trimble.1@research.gla.ac.uk}}
    }
}
